# Reproducible Research: Peer Assessment 1

## Loading and preprocessing the data
```{r}
data <- read.csv("activity.csv")
```

## What is mean total number of steps taken per day?

```{r}
dailysteps <- tapply(data$steps, data$date, sum)
dailysteps
```


For this part of the assignment, you can ignore the missing values in the dataset.

Make a histogram of the total number of steps taken each day
```{r}
hist(dailysteps)
```

Calculate and report the mean and median total number of steps taken per day
```{r}
dailymean <- mean(dailysteps, na.rm=TRUE)
dailymean
dailymedian <- median(dailysteps, na.rm=TRUE)
dailymedian
```

## What is the average daily activity pattern?

Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)

```{r}
intervalavg <- tapply(data$steps, data$interval, mean, na.rm=TRUE)
plot(intervalavg, type= "l", main="Average number of steps taken per interval")
```

Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r}
max(intervalavg)
intervalavg
```
We can see from the list above, that the max average number of steps (206,2) is contained by interval "835", which is 8:35-8:40 AM.


## Imputing missing values

Note that there are a number of days/intervals where there are missing values (coded as NA). The presence of missing days may introduce bias into some calculations or summaries of the data.

Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with NAs)
```{r}
NArows <- sum(is.na(data[,1]))
NArows
```

Devise a strategy for filling in all of the missing values in the dataset. The strategy does not need to be sophisticated. For example, you could use the mean/median for that day, or the mean for that 5-minute interval, etc.

Create a new dataset that is equal to the original dataset but with the missing data filled in.

Coding strategy: Since each day has 288 intervals, NA-values are filled with the value "dailymean/288" 
```{r}
for (i in 1:nrow(data)){
    if (is.na(data[i,1])) {
       data[i,1] = dailymean/288 # 288 is the number of #intervals per day
    }
}
```

Make a histogram of the total number of steps taken each day and Calculate and report the mean and median total number of steps taken per day. Do these values differ from the estimates from the first part of the assignment? What is the impact of imputing missing data on the estimates of the total daily number of steps?

```{r}
dailysteps2 <- tapply(data$steps, data$date, sum)
dailysteps2
mean(dailysteps2)
median(dailysteps2)
hist(dailysteps2)
```

